Using temperature distributions of active regions to investigate flare activity

### 2015-01-19 paper.tex
Minor additions

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
The specific active regions investigated are listed in Table X along with the flares associated with each. % Include a table of the flares looked at, when they occured and which active region they're associated with.
The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

\subsubsection{Long-term temperature distribution}
For each flare event investigated, a temperature map was calculated for a 50x50 arcsec area around the corresponding active region at 1-minute intervals for the hour preceding the event.
The times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
How the temperature distribution changes with time was then compared to when associated flares occur for each active region.
The mean (and standard deviation? percentiles?) of the temperature map was calculated at each time step and these values were plotted for each flare.

>>>>

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
The specific active regions investigated are listed in Table X along with the flares associated with each. % Include a table of the flares looked at, when they occured and which active region they're associated with.

\begin{table}
	\centering
		\begin{tabular}

		\end{tabular}
	\caption{Times and associated active regions of solar flares studied}
	\label{tab:flares}
	% Many of these won't be there because of not working
\end{table}

The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the 30 minutes leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

Sample temperature maps demonstrating the tracking of the active regions are shown in Figures Y - Z

\subsubsection{Long-term temperature distribution}
For each flare event investigated, a temperature map was calculated for a 50x50 arcsec area around the corresponding active region at 1-minute intervals for the hour preceding the event. % 150x150 arcsec I think? change this
The times of the flares and the locations of the active regions on the solar disk were obtained by querying the Heliophysics Events Knowledgebase (HEK).
How the temperature distribution changes with time was then compared to when associated flares occur for each active region.
The mean (and standard deviation? percentiles?, etc) of the temperature map was calculated at each time step and these values were plotted for each flare.
